?????????????????

### 2022-10-12 article_1/New_model_LaTeX/content.tex
Add Total Grad function and optimize the code

%\documentclass[paper]{geophysics}
\documentclass[manuscript,revised]{geophysics}

\usepackage{setspace}
\usepackage[colorlinks]{hyperref}
\hypersetup{colorlinks=true,linkcolor={blue},citecolor={blue},urlcolor={red}}

\usepackage{amsmath}
\usepackage[utf8x]{inputenc}
\usepackage{graphicx}
\graphicspath{ {./images/} } % images path

\usepackage[nameinlink, capitalise, noabbrev]{cleveref} % enhance refs

\usepackage[document]{ragged2e} % to justify text

%\usepackage{ragged2e}
\DeclareCaptionJustification{justified}{\justifying} 			% to justify figure caption
%\captionsetup{compatibility=false,justification=justified} 		% to justify figure caption
%\DeclareCaptionFormat{custom}{\textbf{#1#2}\textit{\small #3}}
\DeclareCaptionFormat{custom}{\textbf{#1#2}{\small #3}}
\captionsetup{compatibility=false, justification=justified, format=custom}

% An example of defining macros
\newcommand{\rs}[1]{\mathstrut\mbox{\scriptsize\rm #1}}
\newcommand{\rr}[1]{\mbox{\rm #1}}

% found it here: https://stackoverflow.com/questions/70705684/latex-get-figure-caption-to-align-with-image
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage{blindtext} % Package to generate dummy text throughout this template 
\usepackage[sc]{mathpazo} % Use the Palatino font
\usepackage[T1]{fontenc} % Use 8-bit encoding that has 256 glyphs
\linespread{1.05} % Line spacing - Palatino needs more space between lines
\usepackage{microtype} % Slightly tweak font spacing for aesthetics
\usepackage[english]{babel} % Language hyphenation and typographical rules

\usepackage[hmarginratio=1:1,top=32mm,columnsep=20pt]{geometry} % Document margins
\usepackage{lettrine} % The lettrine is the first enlarged letter at the beginning of the text

\usepackage{enumitem} % Customized lists
\setlist[itemize]{noitemsep} % Make itemize lists more compact

\usepackage{fancyhdr} % Headers and footers
\pagestyle{fancy} % All pages have headers and footers
\fancyhead{} % Blank out the default header
\fancyfoot{} % Blank out the default footer
\fancyhead[L]{Manuscript} % Custom header text
\fancyfoot[RO,LE]{\thepage} % Custom footer text

\setlength\parindent{24pt}
%\usepackage{float}
\usepackage{floatrow}
\usepackage{pdfpages}
\newsavebox\mysavebox
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

\title{?????????????????}
\renewcommand{\thefootnote}{\fnsymbol{footnote}} 
\ms{GEO-Example} % manuscript number

\address{
\footnotemark[1]BP UTG, \\
200 Westlake Park Blvd, \\
Houston, TX, 77079 \\
\footnotemark[2]Bureau of Economic Geology, \\
John A. and Katherine G. Jackson School of Geosciences \\
The University of Texas at Austin \\
University Station, Box X \\
Austin, TX 78713-8924}

\author{Gelson Ferreira de Souza-Junior\footnotemark[1], Ricardo Ivan Ferreira da Trindade\footnotemark[1],  Leonardo Uieda\footnotemark[2]}
\date{June 2022}
\footer{Example}
\lefthead{Dellinger \& Fomel}
\righthead{\emph{Geophysics} example}

\maketitle
\justify

\begin{abstract}
\begin{singlespace}
Paleomagnetism is the main tool used in paleogeographic reconstructions, in which directional information of the past magnetic field is retrieved from ferromagnetic grains (l.s). Magnetic minerals have a wide range of size and composition that influence their magnetic properties and, consequently, their ability to record the directions of paleomagnetic fields. The signals obtained with classical paleomagnetic methodologies are vector averages that include all magnetic grains present in the samples, including the stable and unstable carriers. To improve the quality of the magnetic signal, it would be necessary to individually identify the magnetizations of the carriers of remanent magnetization, in order to isolate only the good registers of the geomagnetic field. This would allow obtaining more reliable paleomagnetic information, as well as possibly being effective for the paleomagnetic study of older rocks (e.g., Archean rocks), meteorites and even bodies with complex geological evolution. Therefore, this project aims to apply magnetic microscopy to identify the remanent magnetization directions of stable magnetic grains and, subsequently, invert these data in an attempt to recover the individual paleomagnetic directions of the magnetic carriers present in the thin-sections. If successful, a new precision methodology for paleomagnetic data acquisition will be implemented.

\noindent{\textbf{Keywords}: Paleomagnetism, magnetic microscopy, Euler deconvolution, inversion of magnetic data.}
\end{singlespace}
\end{abstract}

@@

\noindent{Assuming that the ferromagnetic minerals (\emph{l.s.}) that give rise to the observed magnetization component data vector ${\bar{B}}_z$ can be approximated by a set of L uniformly magnetized spheres with known coordinates ($xc_j$, $yc_j$, $zc_j$), j = 1, 2, ..., L, of their centers. Also assuming that there is no induced magnetization component, only that of the NRM. Under these assumptions, a superdetermined inverse linear problem is formulated to estimate the vector of parameters $\bar{h}$ (\cref{eq:sphere9}) from the observed data ${\bar{B}}_z and \bar{\bar{M}}$, the latter being obtained previously with the Euler Deconvolution.}

@@

@@

\begin{singlespace}
\doublespacing
\bibliographystyle{agu}  % style file is seg.bst
\bibliography{article1}
\end{singlespace}
\end{document}

>>>>

@@

\noindent{Assuming that the ferromagnetic minerals (\emph{l.s.}) that give rise to the observed magnetization component data vector ${\bar{B}}_z$ can be approximated by a set of L uniformly magnetized spheres with known coordinates ($xc_j$, $yc_j$, $zc_j$), j = 1, 2, ..., L, of their centers. Also assuming that there is no induced magnetization component, only that of the NRM. Under these assumptions, a superdetermined inverse linear problem is formulated to estimate the vector of parameters $\bar{h}$ (\cref{eq:sphere9}) from the observed data ${\bar{B}}_z$ and $\bar{\bar{M}}$, the latter being obtained previously with the Euler Deconvolution.}

@@

%%%
\subsection{Synthetic Data}

\noindent{We applied the proposed method in a numerical simulation of a geological thin-section of dimensions 1000 μm x 1000 μm in a regular grid (1000 x 1000) for estimating the magnetization directions of four spherical sources uniformly magnetized (but different directions), according to \cref{tab:directmodel}. Totaling an observation number N = $10^6$ obtained at a sensor-sample distance of 5 μm and a spacing of 1 μm. Subsequently, a pseudorandom noise of normal Gaussian distribution, with a zero mean and standard variation ≅ 5\% of the anomaly amplitude, was added to the data as shown in Figure XX.}

\floatsetup[table]{capposition=top} % to put the caption on the top of the table

% If you use beamer only pass "xcolor=table" option, i.e. \documentclass[xcolor=table]{beamer}
\begin{table}[htbp]
\caption{Initial position and magnetization parameters for each spherical source.}
\label{tab:directmodel}
\centering
\begin{tabular}[width=1.0\textwidth]{ccccccc}
\rowcolor[HTML]{E7E7E7} 
\cellcolor[HTML]{E7E7E7}                         & \multicolumn{3}{c}{\cellcolor[HTML]{E7E7E7}Center coordinates} & \multicolumn{3}{c}{\cellcolor[HTML]{E7E7E7}Magnetization} \\
\rowcolor[HTML]{E7E7E7} 
\multirow{-2}{*}{\cellcolor[HTML]{E7E7E7}Sphere} & X (µm)              & Y (µm)             & Z (µm)             & Q (A/m)            & D (°)            & I (°)            \\
1                                                & 250                 & 250                & 8.50               & 6.0                & -140             & -30              \\
\rowcolor[HTML]{E7E7E7} 
2                                                & 500                 & 500                & 10.0               & 6.0                & 0                & 62               \\
3                                                & 750                 & 750                & 5.30               & 6.0                & -70              & -50              \\
\rowcolor[HTML]{E7E7E7} 
4                                                & 200                 & 800                & 7.75               & 6.0                & 125              & 22              
\end{tabular}
\end{table}

\subsubsection{Euler Solution}

\noindent{The first step is to calculate the magnetic horizontal gradient in order to isolate the window data of each source. In the horizontal gradient, the magnetic anomaly caused by a body tends to overlap its limits, thus obtaining a robust positioning \citep{Blakely1996}.  \cite{VanderWalt2014}.}

\begin{table}[htbp]
\caption{Central positions of sources input vs Euler deconvolution solutions.}
\label{tab:eulerresults}
\centering
\begin{tabular}[width=1.0\textwidth]{ccccccc}
\rowcolor[HTML]{E7E7E7} 
\cellcolor[HTML]{E7E7E7}                         & \multicolumn{3}{c}{\cellcolor[HTML]{E7E7E7}Posição do Centro de   Entrada} & \multicolumn{3}{c}{\cellcolor[HTML]{E7E7E7}Solução de Euler} \\
\rowcolor[HTML]{E7E7E7} 
\multirow{-2}{*}{\cellcolor[HTML]{E7E7E7}Esfera} & X (µm)                  & Y (µm)                  & Z (µm)                 & X (µm)             & Y (µm)             & Z (µm)             \\
1                                                & 250                     & 250                     & 8.50                   & 249.144984         & 250.084691         & 8.17863468         \\
\rowcolor[HTML]{E7E7E7} 
2                                                & 500                     & 500                     & 10.0                   & 500.213134         & 500.443637         & 9.85904976         \\
3                                                & 750                     & 750                     & 5.30                   & 749.873747         & 750.127834         & 5.26685529         \\
\rowcolor[HTML]{E7E7E7} 
4                                                & 200                     & 800                     & 7.75                   & 200.177971         & 800.331017         & 7.82974687        
\end{tabular}
\end{table}

\begin{table}[htbp]
\caption{Input magnetization directions vs inversion solutions and their error propagation.}
\label{tab:inversionresults}
\centering
\begin{tabular}[width=1.0\textwidth]{ccccccc}
\rowcolor[HTML]{E7E7E7} 
\cellcolor[HTML]{E7E7E7}                         & \multicolumn{2}{c}{\cellcolor[HTML]{E7E7E7}Direção de Entrada} & \multicolumn{4}{c}{\cellcolor[HTML]{E7E7E7}Direções Recuperadas e   Incertezas} \\
\rowcolor[HTML]{E7E7E7} 
\multirow{-2}{*}{\cellcolor[HTML]{E7E7E7}Esfera} & D (°)                          & I (°)                         & D (°)               & $\sigma$ D (°)            & I (°)             & $\sigma$ I (°)           \\
1                                                & -140                           & -30                           & -137.0294           & ± 0.7641          & -32.6550          & ± 0.5169          \\
\rowcolor[HTML]{E7E7E7} 
2                                                & 0                              & 62                            & 2.5167              & ± 1.5004          & 60.5473           & ± 0.6917          \\
3                                                & -70                            & -50                           & -68.3316            & ± 0.6752          & -49.0172          & ± 0.3923          \\
\rowcolor[HTML]{E7E7E7} 
4                                                & 125                            & 22                            & 124.8320            & ± 0.6449          & 21.9940           & ± 0.4515         
\end{tabular}
\end{table}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Data and code availability}

The Python source code used to produce all results and figures presented here
is available at
\url{https://doi.org/10.6084/m9.figshare.13604360} and
\url{https://github.com/compgeolab/eql-gradient-boosted}
under the BSD 3-clause open-source license.

The gradient-boosted equivalent sources implementation is based on the
equivalent source code in the Harmonica library \citep{harmonica2020}.
Other software used in this study includes:
Pooch \citep{pooch2020} for downloading and caching datasets,
Verde \citep{verde2018} for block reductions and coordinate manipulations,
Boule \citep{boule2020} for normal gravity calculations,
xarray \citep{xarray2017} and Numpy \citep{numpy2020} for handling
multidimensional arrays and numerical computations,
Numba \citep{numba2015} for just-in-time compilation and parallelization,
scikit-learn \citep{sklearn2011} for cross-validation,
Matplotlib \citep{matplotlib2007} and PyGMT \citep{pygmt2020} for generating
the figures and maps,
and the Jupyter notebook programming environment \citep{jupyter2016}.
Harmonica, Boule, Pooch, and Verde are part of the Fatiando a Terra project
\citep{fatiando2013}.

All datasets used are open-access and publicly available.
The synthetic surveys were generated using
a public domain gravity dataset for Southern Africa distributed by the
NOAA NCEI (\url{https://www.ngdc.noaa.gov/mgg/gravity/gravity.html})
and the Great Britain Aeromagnetic
Survey distributed by the
British Geological Survey (BGS) under an Open Government License
(\url{https://www.bgs.ac.uk/products/geophysics/aeromagneticRegional.html}).
The shaded relief in Fig.~\ref{fig:australia} is the SRTM15+ dataset by
\citet{tozer2019}.
The Australian ground gravity
data is based on a compilation distributed by Geoscience Australia under a
Creative Commons Attribution 4.0 International Licence \citep{wynne2018}  which
was filtered and referenced to the WGS84 ellipsoid by
\citet{australia_compilation} and is distributed under the same license
(\url{https://doi.org/10.6084/m9.figshare.13643837}).

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Acknowledgements}

We are indebted to the developers and maintainers of the open-source software
without which this work would not have been possible.
We would also like to thank Editor Frederik Simons, Assistant Editor Fern
Storey, and two anonymous reviewers for their constructive comments.
S.R. Soler is supported by a scholarship from CONICET, Argentina.
This work contains British Geological Survey materials ©~UKRI.
S.R. Soler and L. Uieda jointly developed the initial idea, analysed the
results, and wrote the paper. S.R. Soler produced all results and developed the
software implementation with the assistance of L. Uieda.
